---
title: "lab"
output: html_document
date: "2023-09-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
library(tidyverse)
devtools::load_all()
```

## Authentification

```{r}
token <- req_token(user = "benguinaudeau.bsky.social", 
                   password = "")
```

## Test value used in the unit tests

```{r}
test_val <- list(
  handle1 = "aurman21.bsky.social",
  handle2 = "profmusgrave.bsky.social",
  ownhandle = "benguinaudeau.bsky.social",
  
  list1 = "at://did:plc:kyttpb6um57f4c2wep25lqhq/app.bsky.graph.list/3k4diugcw3k2p",
  
  feed_gen1 = 'at://did:plc:kyttpb6um57f4c2wep25lqhq/app.bsky.feed.generator/aaaevewijfbqy', # Polisky
  feed_gen2 = 'at://did:plc:kyttpb6um57f4c2wep25lqhq/app.bsky.feed.generator/aaalfodybabzy', # Skynet
  post_uri = 'at://did:plc:kyttpb6um57f4c2wep25lqhq/app.bsky.feed.post/3k7vuxaw6ew2n',
  post_uri = "https://bsky.app/profile/aoc.bsky.social/post/3jzszuihulm2m",
  feed_gens = c(feed_gen1, feed_gen2),
  aoc_post_1 = "at://did:plc:p7gxyfr5vii5ntpwo7f6dhe2/app.bsky.feed.post/3k26nvf2xdz2m",
  aoc_post_2 = "at://did:plc:p7gxyfr5vii5ntpwo7f6dhe2/app.bsky.feed.post/3k24roywgx726",
  aoc_posts = c(aoc_post_1, aoc_post_2),
  
  feed1 = "at://did:plc:kyttpb6um57f4c2wep25lqhq/app.bsky.feed.generator/aaalfodybabzy",
  feed = "at://did:plc:kyttpb6um57f4c2wep25lqhq/app.bsky.feed.generator/aaaevewijfbqy"
)
usethis::use_data(test_val)
```

## Get all lexicons

### Update lexicons

```{r}
# list_lexicons <- github_ls(repo = "https://api.github.com/repos/bluesky-social/atproto/contents", 
#                            folder = "lexicons") %>%
#   str_remove("lexicons") %>%
#   set_names(
#     fs::path_file(.) |>
#       str_remove(".json")
#   ) |>
#   as.list()
# usethis::use_data(list_lexicons)
```

### Read all lexicons

```{r}
all <- list_lexicons %>%
  map_dfr(~{
    tibble::tibble(
      id = .x,
      lexicon = list(read_lexicon(.x))
    ) %>%
      mutate(
        type = lexicon[[1]] %>%
          purrr::pluck("defs", "main", "type")
      )
  })
```


### Check lexicons type

```{r}
all %>%
  add_count(type) %>%
  distinct(type, .keep_all = T) %>%
  rename(example = id) %>%
  arrange(desc(n))
```

## Generate functions

### Generate the functions

```{r}
# dput(names(list_lexicons[str_detect(names(list_lexicons), "^get")]))

list_lexicons %>% #bashR::simule_map(4)
  walk(~{
    glimpse(.x)
    build_function(lexicon = .x, out_file = "R/test_generated.r" )
  })

```


## Testing function

```{r}
arg_list <-  ls("package:atr") %>%
  str_subset("^(app|com)") %>%
  map_dfr(~{
    tibble::tibble(
      fun = .x,
      param = formalArgs(get(.x, envir = asNamespace('atr')))
    )
  })

arg_list %>%
  filter(!param %in% c("actor", "actors", "limit", "cursor")) %>%
  arrange(param) %>%
  glimpse
```

## Testing post endpoitn 

```{r}
repo <- "benguinaudeau.bsky.social"
collection <- "app.bsky.feed.post"

record <- list(
    "text" = "Testing around",
    "createdAt" = format(as.POSIXct(Sys.time(), tz = "UTC"), "%Y-%m-%dT%H:%M:%OS6Z")
    )

resp <- com_atproto_repo_create_record(repo, collection, record, .token = token)
resp
```

## Manual testing


```{r}
app_bsky_actor_get_preferences(.token = token)

app_bsky_actor_get_profile(actor = handle1, .token = token)
app_bsky_actor_get_profiles(actors = c(handle1, handle2), .token = token)

app_bsky_actor_get_suggestions(.token = token)

app_bsky_notification_get_unread_count(.token = token)
app_bsky_notification_list_notifications(.token = token)
res1 <-app_bsky_notification_list_notifications(limit = 5, .token = token)
res2 <-app_bsky_notification_list_notifications(limit = 5, cursor = res1$cursor, .token = token)

app_bsky_graph_get_followers(actor = handle1, .token = token)
res1 <- app_bsky_graph_get_followers(actor = handle1, limit = 5, .token = token)
res2 <- app_bsky_graph_get_followers(actor = handle1, limit = 5, cursor = res2$cursor, .token = token)

app_bsky_graph_get_follows(actor = handle1, .token = token)
res1 <- app_bsky_graph_get_follows(actor = handle1, limit = 5, .token = token)
res2 <- app_bsky_graph_get_follows(actor = handle1, limit = 5, cursor = res2$cursor, .token = token)


posts <- app_bsky_feed_get_actor_feeds("profmusgrave.bsky.social", .token = token)
posts$feeds %>%
  map_chr(~.x$uri)


app_bsky_graph_get_list(list = list1, .token = token)
app_bsky_feed_get_list_feed(list = list1, .token = token)
app_bsky_graph_get_lists(actor = handle2, .token = token)
app_bsky_graph_get_list_blocks(.token = token)
app_bsky_graph_get_list_mutes(.token = token)

# app_bsky_feed_get_actor_feeds(actor = )
app_bsky_feed_get_author_feed(actor = handle2, .token = token)
app_bsky_feed_get_author_feed(actor = handle2, filter = "posts_with_media", .token = token)

# Only for own account
app_bsky_feed_get_actor_likes(actor = handle3, .token = token)

# Generator


app_bsky_feed_get_feed(feed = feed_gen1, .token = token)
app_bsky_feed_get_feed_generator(feed = feed_gen1, .token = token)
app_bsky_feed_get_feed_generators(feed = feed_gens, .token = token)

app_bsky_feed_get_likes(uri = feed_gen1, .token = token)
app_bsky_feed_get_likes(uri = post_uri, .token = token)
app_bsky_feed_get_reposted_by(uri = post_uri, .token = token)

app_bsky_feed_get_suggested_feeds(.token = token)

app_bsky_feed_get_posts(uris = c(post_uri), .token = token)


# Unclear
# app_bsky_feed_get_feed_skeleton(feed = feed_gen1)

```



## Automatize Testing

```{r}
# app_bsky_actor_get_profile <- function(actor){
#   
#   get_params <- match.call(expand.dots = FALSE) |>
#     flatten_query_params()
#   
#   list(
#     scheme = 'https', 
#     hostname = glue::glue('bsky.social/xrpc/app.bsky.actor.getProfile'),
#     query = as.list(get_params)
#   ) |>
#     app_bsky_actor_get_profile_int() |> 
#     httr2::resp_body_json()
# }

# app_bsky_actor_get_profile_int <- function(all_params){
#   all_params |>
#     httr2::url_build() |>
#     httr2::request() |> 
#     httr2::req_method('GET') |>
#     httr2::req_headers(
#       Authorization = paste0('Bearer ', token$accessJwt)
#     ) |> 
#     httr2::req_perform()
# }

req <- list(
  scheme = 'https', 
  hostname = glue::glue('bsky.social/xrpc/app.bsky.actor.getProfile'),
  query = list(actor = "benguinaudeau.bsky.social")
) %>%
  app_bsky_actor_get_profile_int

# <httr2_response>
# GET https://bsky.social/xrpc/app.bsky.actor.getProfile?actor=benguinaudeau.bsky.social
# Status: 200 OK
# Content-Type: application/json
# Body: In memory (785 bytes)

httr2::resp_body_string(req)

# "{\"did\":\"did:plc:vuvsifrusnjsys7mhkpk662u\",\"handle\":\"benguinaudeau.bsky.social\",\"displayName\":\"Benjamin Guinaudeau\",\"description\":\"Postdoc @CSMaP_NYU. \\n\\nPolitics, data science, and hacking stuff in #rstats. \\n\\n🇫🇷 in 🇩🇪/🇨🇦 he/him\\n\\nPrev: PoliSci PhD @UniKonstanz and @Meta CDS\\n\\nWebsite: http://benguinaudeau.com\",\"avatar\":\"https://av-cdn.bsky.app/img/avatar/plain/did:plc:vuvsifrusnjsys7mhkpk662u/bafkreieahfe2ttg5dfk7btivcpr2onoztgzdjh4valkxqpji42qpkmwacq@jpeg\",\"banner\":\"https://av-cdn.bsky.app/img/banner/plain/did:plc:vuvsifrusnjsys7mhkpk662u/bafkreigv4ycltavnhofcjgkrzhxuoaa6eotimeocfdqmirc2dxfrvfbsuu@jpeg\",\"followsCount\":129,\"followersCount\":223,\"postsCount\":15,\"indexedAt\":\"2023-09-19T00:08:33.661Z\",\"viewer\":{\"muted\":false,\"blockedBy\":false},\"labels\":[]}"

app_bsky_actor_get_profile(actor = "benguinaudeau.bsky.social") %>%
  jsonlite::toJSON()

{"did":["did:plc:vuvsifrusnjsys7mhkpk662u"],"handle":["benguinaudeau.bsky.social"],"displayName":["Benjamin Guinaudeau"],"description":["Postdoc @CSMaP_NYU. \n\nPolitics, data science, and hacking stuff in #rstats. \n\n🇫🇷 in 🇩🇪/🇨🇦 he/him\n\nPrev: PoliSci PhD @UniKonstanz and @Meta CDS\n\nWebsite: http://benguinaudeau.com"],"avatar":["https://av-cdn.bsky.app/img/avatar/plain/did:plc:vuvsifrusnjsys7mhkpk662u/bafkreieahfe2ttg5dfk7btivcpr2onoztgzdjh4valkxqpji42qpkmwacq@jpeg"],"banner":["https://av-cdn.bsky.app/img/banner/plain/did:plc:vuvsifrusnjsys7mhkpk662u/bafkreigv4ycltavnhofcjgkrzhxuoaa6eotimeocfdqmirc2dxfrvfbsuu@jpeg"],"followsCount":[129],"followersCount":[223],"postsCount":[15],"indexedAt":["2023-09-19T00:08:33.661Z"],"viewer":{"muted":[false],"blockedBy":[false]},"labels":[]} 

```





```{r}
all_funs <- unique(arg_list$fun) %>%
  str_subset("^(app|com)")

fun_name <- sample(all_funs, 1)

header <- c('---\ntitle: "lab"\noutput: html_document\ndate: "2023-09-27"\n---\n\n```{r setup, include=FALSE}\nknitr::opts_chunk$set(echo = TRUE)\n```')

final_output <- all_funs %>%
  map(~{
    fun_name <- .x
    
    output <- c(glue::glue("## {fun_name}"), "", "```{r}")
    
    fun <- get(fun_name, envir = asNamespace('atr'))
    args <- formalArgs(fun)
    
    params <- list()
    if("actor" %in% args){
      params[["actor"]] <- c("ownhandle", "handle1", "handle2")
    }
    if("actors" %in% args){
      params[["actors"]] <- c(" c(handle1, handle2)")
    }
    if("limit" %in% args){
      params[["limit"]] <- c("NULL", "5", "10")
    }
    if("uri" %in% args){
      params[["uri"]] <- c("feed_gen1", "feed_gen2", "list1", "post_uri")
    }
    if("uris" %in% args){
      params[["uris"]] <- c("aoc_posts")
    }
    if("algorithm" %in% args){
      # params[["uris"]] <- c("aoc_posts")
    }
    if("feed" %in% args){
      params[["feed"]] <- c("feed1")
    }
    if("feeds" %in% args){
      params[["feeds"]] <- c("c(feed1, feed2)")
    }
    if("depth" %in% args){
      params[["depth"]] <- c("NULL", "0", "3", "5", "10")
    }
    if("parentHeight" %in% args){
      params[["parentHeight"]] <- c("NULL", "0", "80", "160")
    }
    if("filter" %in% args){
      params[["filter"]] <- c("NULL", "posts_with_replies", "posts_no_replies", "posts_with_media")
    }
    if("cursor" %in% args){
      params[["cursor"]] <- c(T, F)
    }
    
    param_grid <- expand_grid(!!!params) %>%
      mutate(index = row_number())
    
    out <- param_grid %>%
      split(1:nrow(.)) %>%
      map_chr(~{
        index <- .x$index
        
        .x[["index"]] <- NULL
        .x[["cursor"]] <- NULL
        
        arg_declaration <- .x %>%
          discard(~.x == "NULL") %>%
          imap_chr(~paste(.y, .x, sep = " = ")) %>%
          paste(collapse = " ,")
        
        glue::glue("{fun_name}({arg_declaration}) # {index}")
      }) %>%
      c(output, ., "```", "", "")
  })

c(header, final_output) %>% 
  reduce(c) %>%
  readr::write_lines("testing.Rmd")
```




I am writting an R package to query data stored and transfered using the AT protocol described on this webpage: https://atproto.com/guides/overview. 

This is many ways similar to the python library atproto: https://github.com/MarshalX/atproto

I have generated the function querying the API and need your help to write unit testing of the functions. Is that understood? 
  


