---
title: "lab"
output: html_document
date: "2023-09-27"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## app_bsky_actor_get_preferences

```{r}
app_bsky_actor_get_preferences() # 1
```


## app_bsky_actor_get_profile

```{r}
app_bsky_actor_get_profile(actor = ownhandle) # 1
app_bsky_actor_get_profile(actor = handle1) # 2
app_bsky_actor_get_profile(actor = handle2) # 3
```


## app_bsky_actor_get_profiles

```{r}
app_bsky_actor_get_profiles(actors =  c(handle1, handle2)) # 1
```


## app_bsky_actor_get_suggestions

```{r}
app_bsky_actor_get_suggestions() # 1
app_bsky_actor_get_suggestions() # 2
app_bsky_actor_get_suggestions(limit = 5) # 3
app_bsky_actor_get_suggestions(limit = 5) # 4
app_bsky_actor_get_suggestions(limit = 10) # 5
app_bsky_actor_get_suggestions(limit = 10) # 6
```


## app_bsky_feed_get_actor_feeds

```{r}
app_bsky_feed_get_actor_feeds(actor = ownhandle) # 1
app_bsky_feed_get_actor_feeds(actor = ownhandle) # 2
app_bsky_feed_get_actor_feeds(actor = ownhandle ,limit = 5) # 3
app_bsky_feed_get_actor_feeds(actor = ownhandle ,limit = 5) # 4
app_bsky_feed_get_actor_feeds(actor = ownhandle ,limit = 10) # 5
app_bsky_feed_get_actor_feeds(actor = ownhandle ,limit = 10) # 6
app_bsky_feed_get_actor_feeds(actor = handle1) # 7
app_bsky_feed_get_actor_feeds(actor = handle1) # 8
app_bsky_feed_get_actor_feeds(actor = handle1 ,limit = 5) # 9
app_bsky_feed_get_actor_feeds(actor = handle1 ,limit = 5) # 10
app_bsky_feed_get_actor_feeds(actor = handle1 ,limit = 10) # 11
app_bsky_feed_get_actor_feeds(actor = handle1 ,limit = 10) # 12
app_bsky_feed_get_actor_feeds(actor = handle2) # 13
app_bsky_feed_get_actor_feeds(actor = handle2) # 14
app_bsky_feed_get_actor_feeds(actor = handle2 ,limit = 5) # 15
app_bsky_feed_get_actor_feeds(actor = handle2 ,limit = 5) # 16
app_bsky_feed_get_actor_feeds(actor = handle2 ,limit = 10) # 17
app_bsky_feed_get_actor_feeds(actor = handle2 ,limit = 10) # 18
```


## app_bsky_feed_get_actor_likes

```{r}
app_bsky_feed_get_actor_likes(actor = ownhandle) # 1
app_bsky_feed_get_actor_likes(actor = ownhandle) # 2
app_bsky_feed_get_actor_likes(actor = ownhandle ,limit = 5) # 3
app_bsky_feed_get_actor_likes(actor = ownhandle ,limit = 5) # 4
app_bsky_feed_get_actor_likes(actor = ownhandle ,limit = 10) # 5
app_bsky_feed_get_actor_likes(actor = ownhandle ,limit = 10) # 6
app_bsky_feed_get_actor_likes(actor = handle1) # 7
app_bsky_feed_get_actor_likes(actor = handle1) # 8
app_bsky_feed_get_actor_likes(actor = handle1 ,limit = 5) # 9
app_bsky_feed_get_actor_likes(actor = handle1 ,limit = 5) # 10
app_bsky_feed_get_actor_likes(actor = handle1 ,limit = 10) # 11
app_bsky_feed_get_actor_likes(actor = handle1 ,limit = 10) # 12
app_bsky_feed_get_actor_likes(actor = handle2) # 13
app_bsky_feed_get_actor_likes(actor = handle2) # 14
app_bsky_feed_get_actor_likes(actor = handle2 ,limit = 5) # 15
app_bsky_feed_get_actor_likes(actor = handle2 ,limit = 5) # 16
app_bsky_feed_get_actor_likes(actor = handle2 ,limit = 10) # 17
app_bsky_feed_get_actor_likes(actor = handle2 ,limit = 10) # 18
```


## app_bsky_feed_get_author_feed

```{r}
app_bsky_feed_get_author_feed(actor = ownhandle) # 1
app_bsky_feed_get_author_feed(actor = ownhandle) # 2
app_bsky_feed_get_author_feed(actor = ownhandle ,filter = posts_with_replies) # 3
app_bsky_feed_get_author_feed(actor = ownhandle ,filter = posts_with_replies) # 4
app_bsky_feed_get_author_feed(actor = ownhandle ,filter = posts_no_replies) # 5
app_bsky_feed_get_author_feed(actor = ownhandle ,filter = posts_no_replies) # 6
app_bsky_feed_get_author_feed(actor = ownhandle ,filter = posts_with_media) # 7
app_bsky_feed_get_author_feed(actor = ownhandle ,filter = posts_with_media) # 8
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 5) # 9
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 5) # 10
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 5 ,filter = posts_with_replies) # 11
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 5 ,filter = posts_with_replies) # 12
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 5 ,filter = posts_no_replies) # 13
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 5 ,filter = posts_no_replies) # 14
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 5 ,filter = posts_with_media) # 15
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 5 ,filter = posts_with_media) # 16
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 10) # 17
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 10) # 18
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 10 ,filter = posts_with_replies) # 19
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 10 ,filter = posts_with_replies) # 20
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 10 ,filter = posts_no_replies) # 21
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 10 ,filter = posts_no_replies) # 22
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 10 ,filter = posts_with_media) # 23
app_bsky_feed_get_author_feed(actor = ownhandle ,limit = 10 ,filter = posts_with_media) # 24
app_bsky_feed_get_author_feed(actor = handle1) # 25
app_bsky_feed_get_author_feed(actor = handle1) # 26
app_bsky_feed_get_author_feed(actor = handle1 ,filter = posts_with_replies) # 27
app_bsky_feed_get_author_feed(actor = handle1 ,filter = posts_with_replies) # 28
app_bsky_feed_get_author_feed(actor = handle1 ,filter = posts_no_replies) # 29
app_bsky_feed_get_author_feed(actor = handle1 ,filter = posts_no_replies) # 30
app_bsky_feed_get_author_feed(actor = handle1 ,filter = posts_with_media) # 31
app_bsky_feed_get_author_feed(actor = handle1 ,filter = posts_with_media) # 32
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 5) # 33
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 5) # 34
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 5 ,filter = posts_with_replies) # 35
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 5 ,filter = posts_with_replies) # 36
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 5 ,filter = posts_no_replies) # 37
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 5 ,filter = posts_no_replies) # 38
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 5 ,filter = posts_with_media) # 39
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 5 ,filter = posts_with_media) # 40
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 10) # 41
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 10) # 42
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 10 ,filter = posts_with_replies) # 43
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 10 ,filter = posts_with_replies) # 44
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 10 ,filter = posts_no_replies) # 45
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 10 ,filter = posts_no_replies) # 46
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 10 ,filter = posts_with_media) # 47
app_bsky_feed_get_author_feed(actor = handle1 ,limit = 10 ,filter = posts_with_media) # 48
app_bsky_feed_get_author_feed(actor = handle2) # 49
app_bsky_feed_get_author_feed(actor = handle2) # 50
app_bsky_feed_get_author_feed(actor = handle2 ,filter = posts_with_replies) # 51
app_bsky_feed_get_author_feed(actor = handle2 ,filter = posts_with_replies) # 52
app_bsky_feed_get_author_feed(actor = handle2 ,filter = posts_no_replies) # 53
app_bsky_feed_get_author_feed(actor = handle2 ,filter = posts_no_replies) # 54
app_bsky_feed_get_author_feed(actor = handle2 ,filter = posts_with_media) # 55
app_bsky_feed_get_author_feed(actor = handle2 ,filter = posts_with_media) # 56
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 5) # 57
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 5) # 58
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 5 ,filter = posts_with_replies) # 59
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 5 ,filter = posts_with_replies) # 60
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 5 ,filter = posts_no_replies) # 61
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 5 ,filter = posts_no_replies) # 62
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 5 ,filter = posts_with_media) # 63
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 5 ,filter = posts_with_media) # 64
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 10) # 65
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 10) # 66
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 10 ,filter = posts_with_replies) # 67
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 10 ,filter = posts_with_replies) # 68
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 10 ,filter = posts_no_replies) # 69
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 10 ,filter = posts_no_replies) # 70
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 10 ,filter = posts_with_media) # 71
app_bsky_feed_get_author_feed(actor = handle2 ,limit = 10 ,filter = posts_with_media) # 72
```


## app_bsky_feed_get_feed

```{r}
app_bsky_feed_get_feed(feed = feed1) # 1
app_bsky_feed_get_feed(feed = feed1) # 2
app_bsky_feed_get_feed(limit = 5 ,feed = feed1) # 3
app_bsky_feed_get_feed(limit = 5 ,feed = feed1) # 4
app_bsky_feed_get_feed(limit = 10 ,feed = feed1) # 5
app_bsky_feed_get_feed(limit = 10 ,feed = feed1) # 6
```


## app_bsky_feed_get_feed_generator

```{r}
app_bsky_feed_get_feed_generator(feed = feed1) # 1
```


## app_bsky_feed_get_feed_generators

```{r}
app_bsky_feed_get_feed_generators(feeds = c(feed1, feed2)) # 1
```


## app_bsky_feed_get_feed_skeleton

```{r}
app_bsky_feed_get_feed_skeleton(feed = feed1) # 1
app_bsky_feed_get_feed_skeleton(feed = feed1) # 2
app_bsky_feed_get_feed_skeleton(limit = 5 ,feed = feed1) # 3
app_bsky_feed_get_feed_skeleton(limit = 5 ,feed = feed1) # 4
app_bsky_feed_get_feed_skeleton(limit = 10 ,feed = feed1) # 5
app_bsky_feed_get_feed_skeleton(limit = 10 ,feed = feed1) # 6
```


## app_bsky_feed_get_likes

```{r}
app_bsky_feed_get_likes(uri = feed_gen1) # 1
app_bsky_feed_get_likes(uri = feed_gen1) # 2
app_bsky_feed_get_likes(uri = feed_gen2) # 3
app_bsky_feed_get_likes(uri = feed_gen2) # 4
app_bsky_feed_get_likes(uri = list1) # 5
app_bsky_feed_get_likes(uri = list1) # 6
app_bsky_feed_get_likes(uri = post_uri) # 7
app_bsky_feed_get_likes(uri = post_uri) # 8
app_bsky_feed_get_likes(limit = 5 ,uri = feed_gen1) # 9
app_bsky_feed_get_likes(limit = 5 ,uri = feed_gen1) # 10
app_bsky_feed_get_likes(limit = 5 ,uri = feed_gen2) # 11
app_bsky_feed_get_likes(limit = 5 ,uri = feed_gen2) # 12
app_bsky_feed_get_likes(limit = 5 ,uri = list1) # 13
app_bsky_feed_get_likes(limit = 5 ,uri = list1) # 14
app_bsky_feed_get_likes(limit = 5 ,uri = post_uri) # 15
app_bsky_feed_get_likes(limit = 5 ,uri = post_uri) # 16
app_bsky_feed_get_likes(limit = 10 ,uri = feed_gen1) # 17
app_bsky_feed_get_likes(limit = 10 ,uri = feed_gen1) # 18
app_bsky_feed_get_likes(limit = 10 ,uri = feed_gen2) # 19
app_bsky_feed_get_likes(limit = 10 ,uri = feed_gen2) # 20
app_bsky_feed_get_likes(limit = 10 ,uri = list1) # 21
app_bsky_feed_get_likes(limit = 10 ,uri = list1) # 22
app_bsky_feed_get_likes(limit = 10 ,uri = post_uri) # 23
app_bsky_feed_get_likes(limit = 10 ,uri = post_uri) # 24
```


## app_bsky_feed_get_list_feed

```{r}
app_bsky_feed_get_list_feed() # 1
app_bsky_feed_get_list_feed() # 2
app_bsky_feed_get_list_feed(limit = 5) # 3
app_bsky_feed_get_list_feed(limit = 5) # 4
app_bsky_feed_get_list_feed(limit = 10) # 5
app_bsky_feed_get_list_feed(limit = 10) # 6
```


## app_bsky_feed_get_post_thread

```{r}
app_bsky_feed_get_post_thread(uri = feed_gen1) # 1
app_bsky_feed_get_post_thread(uri = feed_gen1 ,parentHeight = 0) # 2
app_bsky_feed_get_post_thread(uri = feed_gen1 ,parentHeight = 80) # 3
app_bsky_feed_get_post_thread(uri = feed_gen1 ,parentHeight = 160) # 4
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 0) # 5
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 0 ,parentHeight = 0) # 6
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 0 ,parentHeight = 80) # 7
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 0 ,parentHeight = 160) # 8
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 3) # 9
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 3 ,parentHeight = 0) # 10
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 3 ,parentHeight = 80) # 11
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 3 ,parentHeight = 160) # 12
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 5) # 13
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 5 ,parentHeight = 0) # 14
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 5 ,parentHeight = 80) # 15
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 5 ,parentHeight = 160) # 16
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 10) # 17
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 10 ,parentHeight = 0) # 18
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 10 ,parentHeight = 80) # 19
app_bsky_feed_get_post_thread(uri = feed_gen1 ,depth = 10 ,parentHeight = 160) # 20
app_bsky_feed_get_post_thread(uri = feed_gen2) # 21
app_bsky_feed_get_post_thread(uri = feed_gen2 ,parentHeight = 0) # 22
app_bsky_feed_get_post_thread(uri = feed_gen2 ,parentHeight = 80) # 23
app_bsky_feed_get_post_thread(uri = feed_gen2 ,parentHeight = 160) # 24
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 0) # 25
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 0 ,parentHeight = 0) # 26
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 0 ,parentHeight = 80) # 27
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 0 ,parentHeight = 160) # 28
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 3) # 29
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 3 ,parentHeight = 0) # 30
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 3 ,parentHeight = 80) # 31
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 3 ,parentHeight = 160) # 32
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 5) # 33
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 5 ,parentHeight = 0) # 34
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 5 ,parentHeight = 80) # 35
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 5 ,parentHeight = 160) # 36
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 10) # 37
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 10 ,parentHeight = 0) # 38
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 10 ,parentHeight = 80) # 39
app_bsky_feed_get_post_thread(uri = feed_gen2 ,depth = 10 ,parentHeight = 160) # 40
app_bsky_feed_get_post_thread(uri = list1) # 41
app_bsky_feed_get_post_thread(uri = list1 ,parentHeight = 0) # 42
app_bsky_feed_get_post_thread(uri = list1 ,parentHeight = 80) # 43
app_bsky_feed_get_post_thread(uri = list1 ,parentHeight = 160) # 44
app_bsky_feed_get_post_thread(uri = list1 ,depth = 0) # 45
app_bsky_feed_get_post_thread(uri = list1 ,depth = 0 ,parentHeight = 0) # 46
app_bsky_feed_get_post_thread(uri = list1 ,depth = 0 ,parentHeight = 80) # 47
app_bsky_feed_get_post_thread(uri = list1 ,depth = 0 ,parentHeight = 160) # 48
app_bsky_feed_get_post_thread(uri = list1 ,depth = 3) # 49
app_bsky_feed_get_post_thread(uri = list1 ,depth = 3 ,parentHeight = 0) # 50
app_bsky_feed_get_post_thread(uri = list1 ,depth = 3 ,parentHeight = 80) # 51
app_bsky_feed_get_post_thread(uri = list1 ,depth = 3 ,parentHeight = 160) # 52
app_bsky_feed_get_post_thread(uri = list1 ,depth = 5) # 53
app_bsky_feed_get_post_thread(uri = list1 ,depth = 5 ,parentHeight = 0) # 54
app_bsky_feed_get_post_thread(uri = list1 ,depth = 5 ,parentHeight = 80) # 55
app_bsky_feed_get_post_thread(uri = list1 ,depth = 5 ,parentHeight = 160) # 56
app_bsky_feed_get_post_thread(uri = list1 ,depth = 10) # 57
app_bsky_feed_get_post_thread(uri = list1 ,depth = 10 ,parentHeight = 0) # 58
app_bsky_feed_get_post_thread(uri = list1 ,depth = 10 ,parentHeight = 80) # 59
app_bsky_feed_get_post_thread(uri = list1 ,depth = 10 ,parentHeight = 160) # 60
app_bsky_feed_get_post_thread(uri = post_uri) # 61
app_bsky_feed_get_post_thread(uri = post_uri ,parentHeight = 0) # 62
app_bsky_feed_get_post_thread(uri = post_uri ,parentHeight = 80) # 63
app_bsky_feed_get_post_thread(uri = post_uri ,parentHeight = 160) # 64
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 0) # 65
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 0 ,parentHeight = 0) # 66
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 0 ,parentHeight = 80) # 67
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 0 ,parentHeight = 160) # 68
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 3) # 69
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 3 ,parentHeight = 0) # 70
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 3 ,parentHeight = 80) # 71
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 3 ,parentHeight = 160) # 72
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 5) # 73
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 5 ,parentHeight = 0) # 74
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 5 ,parentHeight = 80) # 75
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 5 ,parentHeight = 160) # 76
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 10) # 77
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 10 ,parentHeight = 0) # 78
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 10 ,parentHeight = 80) # 79
app_bsky_feed_get_post_thread(uri = post_uri ,depth = 10 ,parentHeight = 160) # 80
```


## app_bsky_feed_get_posts

```{r}
app_bsky_feed_get_posts(uris = aoc_posts) # 1
```


## app_bsky_feed_get_reposted_by

```{r}
app_bsky_feed_get_reposted_by(uri = feed_gen1) # 1
app_bsky_feed_get_reposted_by(uri = feed_gen1) # 2
app_bsky_feed_get_reposted_by(uri = feed_gen2) # 3
app_bsky_feed_get_reposted_by(uri = feed_gen2) # 4
app_bsky_feed_get_reposted_by(uri = list1) # 5
app_bsky_feed_get_reposted_by(uri = list1) # 6
app_bsky_feed_get_reposted_by(uri = post_uri) # 7
app_bsky_feed_get_reposted_by(uri = post_uri) # 8
app_bsky_feed_get_reposted_by(limit = 5 ,uri = feed_gen1) # 9
app_bsky_feed_get_reposted_by(limit = 5 ,uri = feed_gen1) # 10
app_bsky_feed_get_reposted_by(limit = 5 ,uri = feed_gen2) # 11
app_bsky_feed_get_reposted_by(limit = 5 ,uri = feed_gen2) # 12
app_bsky_feed_get_reposted_by(limit = 5 ,uri = list1) # 13
app_bsky_feed_get_reposted_by(limit = 5 ,uri = list1) # 14
app_bsky_feed_get_reposted_by(limit = 5 ,uri = post_uri) # 15
app_bsky_feed_get_reposted_by(limit = 5 ,uri = post_uri) # 16
app_bsky_feed_get_reposted_by(limit = 10 ,uri = feed_gen1) # 17
app_bsky_feed_get_reposted_by(limit = 10 ,uri = feed_gen1) # 18
app_bsky_feed_get_reposted_by(limit = 10 ,uri = feed_gen2) # 19
app_bsky_feed_get_reposted_by(limit = 10 ,uri = feed_gen2) # 20
app_bsky_feed_get_reposted_by(limit = 10 ,uri = list1) # 21
app_bsky_feed_get_reposted_by(limit = 10 ,uri = list1) # 22
app_bsky_feed_get_reposted_by(limit = 10 ,uri = post_uri) # 23
app_bsky_feed_get_reposted_by(limit = 10 ,uri = post_uri) # 24
```


## app_bsky_feed_get_suggested_feeds

```{r}
app_bsky_feed_get_suggested_feeds() # 1
app_bsky_feed_get_suggested_feeds() # 2
app_bsky_feed_get_suggested_feeds(limit = 5) # 3
app_bsky_feed_get_suggested_feeds(limit = 5) # 4
app_bsky_feed_get_suggested_feeds(limit = 10) # 5
app_bsky_feed_get_suggested_feeds(limit = 10) # 6
```


## app_bsky_feed_get_timeline

```{r}
app_bsky_feed_get_timeline() # 1
app_bsky_feed_get_timeline() # 2
app_bsky_feed_get_timeline(limit = 5) # 3
app_bsky_feed_get_timeline(limit = 5) # 4
app_bsky_feed_get_timeline(limit = 10) # 5
app_bsky_feed_get_timeline(limit = 10) # 6
```


## app_bsky_graph_get_blocks

```{r}
app_bsky_graph_get_blocks() # 1
app_bsky_graph_get_blocks() # 2
app_bsky_graph_get_blocks(limit = 5) # 3
app_bsky_graph_get_blocks(limit = 5) # 4
app_bsky_graph_get_blocks(limit = 10) # 5
app_bsky_graph_get_blocks(limit = 10) # 6
```


## app_bsky_graph_get_followers

```{r}
app_bsky_graph_get_followers(actor = ownhandle) # 1
app_bsky_graph_get_followers(actor = ownhandle) # 2
app_bsky_graph_get_followers(actor = ownhandle ,limit = 5) # 3
app_bsky_graph_get_followers(actor = ownhandle ,limit = 5) # 4
app_bsky_graph_get_followers(actor = ownhandle ,limit = 10) # 5
app_bsky_graph_get_followers(actor = ownhandle ,limit = 10) # 6
app_bsky_graph_get_followers(actor = handle1) # 7
app_bsky_graph_get_followers(actor = handle1) # 8
app_bsky_graph_get_followers(actor = handle1 ,limit = 5) # 9
app_bsky_graph_get_followers(actor = handle1 ,limit = 5) # 10
app_bsky_graph_get_followers(actor = handle1 ,limit = 10) # 11
app_bsky_graph_get_followers(actor = handle1 ,limit = 10) # 12
app_bsky_graph_get_followers(actor = handle2) # 13
app_bsky_graph_get_followers(actor = handle2) # 14
app_bsky_graph_get_followers(actor = handle2 ,limit = 5) # 15
app_bsky_graph_get_followers(actor = handle2 ,limit = 5) # 16
app_bsky_graph_get_followers(actor = handle2 ,limit = 10) # 17
app_bsky_graph_get_followers(actor = handle2 ,limit = 10) # 18
```


## app_bsky_graph_get_follows

```{r}
app_bsky_graph_get_follows(actor = ownhandle) # 1
app_bsky_graph_get_follows(actor = ownhandle) # 2
app_bsky_graph_get_follows(actor = ownhandle ,limit = 5) # 3
app_bsky_graph_get_follows(actor = ownhandle ,limit = 5) # 4
app_bsky_graph_get_follows(actor = ownhandle ,limit = 10) # 5
app_bsky_graph_get_follows(actor = ownhandle ,limit = 10) # 6
app_bsky_graph_get_follows(actor = handle1) # 7
app_bsky_graph_get_follows(actor = handle1) # 8
app_bsky_graph_get_follows(actor = handle1 ,limit = 5) # 9
app_bsky_graph_get_follows(actor = handle1 ,limit = 5) # 10
app_bsky_graph_get_follows(actor = handle1 ,limit = 10) # 11
app_bsky_graph_get_follows(actor = handle1 ,limit = 10) # 12
app_bsky_graph_get_follows(actor = handle2) # 13
app_bsky_graph_get_follows(actor = handle2) # 14
app_bsky_graph_get_follows(actor = handle2 ,limit = 5) # 15
app_bsky_graph_get_follows(actor = handle2 ,limit = 5) # 16
app_bsky_graph_get_follows(actor = handle2 ,limit = 10) # 17
app_bsky_graph_get_follows(actor = handle2 ,limit = 10) # 18
```


## app_bsky_graph_get_list

```{r}
app_bsky_graph_get_list() # 1
app_bsky_graph_get_list() # 2
app_bsky_graph_get_list(limit = 5) # 3
app_bsky_graph_get_list(limit = 5) # 4
app_bsky_graph_get_list(limit = 10) # 5
app_bsky_graph_get_list(limit = 10) # 6
```


## app_bsky_graph_get_list_blocks

```{r}
app_bsky_graph_get_list_blocks() # 1
app_bsky_graph_get_list_blocks() # 2
app_bsky_graph_get_list_blocks(limit = 5) # 3
app_bsky_graph_get_list_blocks(limit = 5) # 4
app_bsky_graph_get_list_blocks(limit = 10) # 5
app_bsky_graph_get_list_blocks(limit = 10) # 6
```


## app_bsky_graph_get_list_mutes

```{r}
app_bsky_graph_get_list_mutes() # 1
app_bsky_graph_get_list_mutes() # 2
app_bsky_graph_get_list_mutes(limit = 5) # 3
app_bsky_graph_get_list_mutes(limit = 5) # 4
app_bsky_graph_get_list_mutes(limit = 10) # 5
app_bsky_graph_get_list_mutes(limit = 10) # 6
```


## app_bsky_graph_get_lists

```{r}
app_bsky_graph_get_lists(actor = ownhandle) # 1
app_bsky_graph_get_lists(actor = ownhandle) # 2
app_bsky_graph_get_lists(actor = ownhandle ,limit = 5) # 3
app_bsky_graph_get_lists(actor = ownhandle ,limit = 5) # 4
app_bsky_graph_get_lists(actor = ownhandle ,limit = 10) # 5
app_bsky_graph_get_lists(actor = ownhandle ,limit = 10) # 6
app_bsky_graph_get_lists(actor = handle1) # 7
app_bsky_graph_get_lists(actor = handle1) # 8
app_bsky_graph_get_lists(actor = handle1 ,limit = 5) # 9
app_bsky_graph_get_lists(actor = handle1 ,limit = 5) # 10
app_bsky_graph_get_lists(actor = handle1 ,limit = 10) # 11
app_bsky_graph_get_lists(actor = handle1 ,limit = 10) # 12
app_bsky_graph_get_lists(actor = handle2) # 13
app_bsky_graph_get_lists(actor = handle2) # 14
app_bsky_graph_get_lists(actor = handle2 ,limit = 5) # 15
app_bsky_graph_get_lists(actor = handle2 ,limit = 5) # 16
app_bsky_graph_get_lists(actor = handle2 ,limit = 10) # 17
app_bsky_graph_get_lists(actor = handle2 ,limit = 10) # 18
```


## app_bsky_graph_get_mutes

```{r}
app_bsky_graph_get_mutes() # 1
app_bsky_graph_get_mutes() # 2
app_bsky_graph_get_mutes(limit = 5) # 3
app_bsky_graph_get_mutes(limit = 5) # 4
app_bsky_graph_get_mutes(limit = 10) # 5
app_bsky_graph_get_mutes(limit = 10) # 6
```


## app_bsky_graph_get_suggested_follows_by_actor

```{r}
app_bsky_graph_get_suggested_follows_by_actor(actor = ownhandle) # 1
app_bsky_graph_get_suggested_follows_by_actor(actor = handle1) # 2
app_bsky_graph_get_suggested_follows_by_actor(actor = handle2) # 3
```


## app_bsky_notification_get_unread_count

```{r}
app_bsky_notification_get_unread_count() # 1
```


## app_bsky_unspecced_get_popular

```{r}
app_bsky_unspecced_get_popular() # 1
app_bsky_unspecced_get_popular() # 2
app_bsky_unspecced_get_popular(limit = 5) # 3
app_bsky_unspecced_get_popular(limit = 5) # 4
app_bsky_unspecced_get_popular(limit = 10) # 5
app_bsky_unspecced_get_popular(limit = 10) # 6
```


## app_bsky_unspecced_get_popular_feed_generators

```{r}
app_bsky_unspecced_get_popular_feed_generators() # 1
app_bsky_unspecced_get_popular_feed_generators() # 2
app_bsky_unspecced_get_popular_feed_generators(limit = 5) # 3
app_bsky_unspecced_get_popular_feed_generators(limit = 5) # 4
app_bsky_unspecced_get_popular_feed_generators(limit = 10) # 5
app_bsky_unspecced_get_popular_feed_generators(limit = 10) # 6
```


## app_bsky_unspecced_get_timeline_skeleton

```{r}
app_bsky_unspecced_get_timeline_skeleton() # 1
app_bsky_unspecced_get_timeline_skeleton() # 2
app_bsky_unspecced_get_timeline_skeleton(limit = 5) # 3
app_bsky_unspecced_get_timeline_skeleton(limit = 5) # 4
app_bsky_unspecced_get_timeline_skeleton(limit = 10) # 5
app_bsky_unspecced_get_timeline_skeleton(limit = 10) # 6
```


## com_atproto_admin_get_invite_codes

```{r}
com_atproto_admin_get_invite_codes() # 1
com_atproto_admin_get_invite_codes() # 2
com_atproto_admin_get_invite_codes(limit = 5) # 3
com_atproto_admin_get_invite_codes(limit = 5) # 4
com_atproto_admin_get_invite_codes(limit = 10) # 5
com_atproto_admin_get_invite_codes(limit = 10) # 6
```


## com_atproto_admin_get_moderation_action

```{r}
com_atproto_admin_get_moderation_action() # 1
```


## com_atproto_admin_get_moderation_actions

```{r}
com_atproto_admin_get_moderation_actions() # 1
com_atproto_admin_get_moderation_actions() # 2
com_atproto_admin_get_moderation_actions(limit = 5) # 3
com_atproto_admin_get_moderation_actions(limit = 5) # 4
com_atproto_admin_get_moderation_actions(limit = 10) # 5
com_atproto_admin_get_moderation_actions(limit = 10) # 6
```


## com_atproto_admin_get_moderation_report

```{r}
com_atproto_admin_get_moderation_report() # 1
```


## com_atproto_admin_get_moderation_reports

```{r}
com_atproto_admin_get_moderation_reports() # 1
com_atproto_admin_get_moderation_reports() # 2
com_atproto_admin_get_moderation_reports(limit = 5) # 3
com_atproto_admin_get_moderation_reports(limit = 5) # 4
com_atproto_admin_get_moderation_reports(limit = 10) # 5
com_atproto_admin_get_moderation_reports(limit = 10) # 6
```


## com_atproto_admin_get_record

```{r}
com_atproto_admin_get_record(uri = feed_gen1) # 1
com_atproto_admin_get_record(uri = feed_gen2) # 2
com_atproto_admin_get_record(uri = list1) # 3
com_atproto_admin_get_record(uri = post_uri) # 4
```


## com_atproto_admin_get_repo

```{r}
com_atproto_admin_get_repo() # 1
```


## com_atproto_server_get_account_invite_codes

```{r}
com_atproto_server_get_account_invite_codes() # 1
```


## com_atproto_server_get_session

```{r}
com_atproto_server_get_session() # 1
```


## com_atproto_sync_get_blob

```{r}
com_atproto_sync_get_blob() # 1
```


## com_atproto_sync_get_checkout

```{r}
com_atproto_sync_get_checkout() # 1
```


## com_atproto_sync_get_head

```{r}
com_atproto_sync_get_head() # 1
```


## com_atproto_sync_get_latest_commit

```{r}
com_atproto_sync_get_latest_commit() # 1
```


