---
title: "Update lexicons and auto gen functions"
format: html
---

```{r}
library(tidyverse)
devtools::load_all()
```

# Update lexicons

This downloads all lexicons, which is how the AT protocol stores the descriptions of API endpoints.

```{r}
rel_paths <- github_ls(repo = "https://api.github.com/repos/bluesky-social/atproto/contents",
                       folder = "lexicons")
lexicons <- sub("lexicons", "", rel_paths, fixed = TRUE)
names(lexicons) <- basename(lexicons) |>
  tools::file_path_sans_ext()

lexicons <- as.list(lexicons)

# save this as a data file
usethis::use_data(list_lexicons, overwrite = TRUE)
```

## Generate functions

Before generating functions, it makes sense to remove the old files in order to start with a clean slate and not have any duplication:

```{r}
list.files(here::here("R"), pattern = "auto_", full.names = TRUE) |> 
  file.remove()
```

The `build_function` downloads a lexicon and generates a function from it.
We can simply iterate through all lexicons, download them if they are not in the package yet, and the create a function for each endpoint:

```{r}
for (lexicon in lexicons) {
  cli::cli_progress_step(lexicon)
  out_file <- paste0(here::here(), "/R/auto_", janitor::make_clean_names(fs::path_dir(lexicon)), ".R")
  build_function(lexicon = lexicon, out_file = out_file) 
}
```
